Compact Particle-Mesh $N$-body Algorithm

### 2016-09-12 ms_caf/ms_caf.tex
update velocity dispersion formula by Xin

\appendix
\section{A. Velocity distribution function}

>>>>

\appendix
\section{A. Velocity distribution function}
To optimize the storage of the velocity field, we need to estimate the velocity dispersion at each snapshot. At non-linear scale, the velocity distribution function is surely non-Gaussian. However, to the first order approximation, we simply assume it as Gaussian and characterized by the variance
\begin{eqnarray}
\sigma_v = \frac{1}{3}  (a H f D)^2 \int d^3q \frac{P_{L}(q)}{q^2} 
\end{eqnarray}
where $a(z)$ is the scale factor, $H(z)$ the Hubble parameter, $D$ is the linear growth factor, $f=d \ln D/d\ln a$, 
and $P_L(k)$ is the linear power spectrum of density contrast at redshift zero.
